### 2018-04-24 tex/paper.tex
Fix some typos

In doing this we are required to refine the model of contracts in a number of ways in order to fit with a radically different context. Let us the following example of an ``escrow'' contract we can explain the motivation more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} involves three participants \haskellinline{1}, \haskellinline{2} and \haskellinline{3}. Participant \haskellinline{1} is to pay an amount of money to participant \haskellinline{2} on receipt of goods from her. Participant \haskellinline{1} pays the money into escrow controlled by participant \haskellinline{3}. There are two options for the money: if two participants agree to \haskellinline{pay} it to \haskellinline{2}, that goes ahead; if, on the other hand, two of the players opt to \haskellinline{refund} the money to \haskellinline{1}, that is done instead. The \haskellinline{When} construct ensures fires when its first argument -- a condition -- becomes true; the second argument, a \haskellinline{Contract} itself, is then performed, and this makes the payment according to the players' \haskellinline{Choice}.

@@

In the traditional model, enforcement of the contract is the responsibility of the legal system. If participant \haskellinline{1} doesn't pay the money into escrow, or participant \haskellinline{3} chooses to keep it for herself, then we can assume that they can be sued for the money and probably damages on top, thus providing both legal and financial incentives for compliance. On the other hand, in the decentralised blockchain model, where there is no central authority, the contract needs to be enforced by design.

This means that we require participants to commit money to cover all possible expenditure \emph{in advance of the contract executing}. In order to make sure that player continue to engage with a contract we ensure urgency by imposing timeouts: money is committed for a finite period, for example, and when waiting for a player to make a commitment we also impose a timeout to ensure that the contract does not become stuck even if one or more of the participants stops interacting with it. We revisit this example in Section~\ref{section:example-escrow} where we show how commitments, timeouts and other features of Marlowe are used to describe this as a self-enforcing contract ``on the blockchain''.

@@

In Nxt~\cite{Nxt}, programmability of the system is provided through a ``fat'' high-level 
API, which is accessible from Nxt clients through a REST interface. The API provides functionality supporting various 
kinds of transactions. The core software itself doesn't support any form of scripting language; rather, users are 
expected to work with the built in transaction types and transactions that support some 250 primitive operations; these 
can be ``scripted'' in a client (only) using a binding to the API, which is available, for instance, in JavaScript.

@@

Contracts can be conceived of as acting in two ways. In a \emph{push} model, contracts are seen to be pro-active, and to 
make things happen. In the case of blockchain, this would include making payments or transactions happen. 
Alternatively, in the \emph{pull} model, contracts enable certain things to happen, such as transactions, but the 
transactions need to be effected by an external player. The pull model makes fewer demands on the blockchain 
implementation than the push model, which requires the contract to be triggered automatically.

>>>>

In doing this, we are required to refine the model of contracts in a number of ways in order to fit with a radically different context. Let us consider the following example of an ``escrow'' contract so that we can explain the motivation more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} involves three participants \haskellinline{1}, \haskellinline{2} and \haskellinline{3}. Participant \haskellinline{1} is to pay an amount of money to participant \haskellinline{2} on receipt of goods from her. Participant \haskellinline{1} pays the money into escrow controlled by participant \haskellinline{3}. There are two options for the money: if two participants agree to \haskellinline{pay} it to \haskellinline{2}, that goes ahead; if, on the other hand, two of the participants opt to \haskellinline{refund} the money to \haskellinline{1}, that is done instead. The \haskellinline{When} construct fires when its first argument -- a condition -- becomes true; the second argument, a \haskellinline{Contract} itself, is then performed, and this makes the payment according to the participants' \haskellinline{Choice}.

@@

In the traditional model, enforcement of the contract is the responsibility of the legal system. If participant \haskellinline{1} does not pay the money into escrow, or participant \haskellinline{3} chooses to keep it for herself, then we can assume that they can be sued for the money and probably damages on top, thus providing both legal and financial incentives for compliance. On the other hand, in the decentralised blockchain model, where there is no central authority, the contract needs to be enforced by design.

This means that we require participants to commit money to cover all possible expenditure \emph{in advance of the contract executing}. In order to make sure that participants continue to engage with a contract, we ensure urgency by imposing timeouts: money is committed for a finite period, for example, and when waiting for a participant to make a commitment we also impose a timeout to ensure that the contract does not become stuck even if one or more of the participants stop interacting with it. We revisit this example in Section~\ref{section:example-escrow} where we show how commitments, timeouts and other features of Marlowe are used to describe this as a self-enforcing contract ``on the blockchain''.

@@

In Nxt~\cite{Nxt}, programmability of the system is provided through a ``fat'' high-level 
API, which is accessible from Nxt clients through a REST interface. The API provides functionality supporting various 
kinds of transactions. The core software itself does not support any form of scripting language; rather, users are 
expected to work with the built in transaction types and transactions that support some 250 primitive operations; these 
can be ``scripted'' in a client (only) using a binding to the API, which is available, for instance, in JavaScript.

@@

Contracts can be conceived of as acting in two ways. In a \emph{push} model, contracts are seen to be pro-active, and to 
make things happen. In the case of blockchain, this would include making payments or transactions happen. 
Alternatively, in the \emph{pull} model, contracts enable certain things to happen, such as transactions, but the 
transactions need to be effected by an external actor. The pull model makes fewer demands on the blockchain 
implementation than the push model, which requires the contract to be triggered automatically.
